---
title: "Research"
output:
  distill::distill_article:
    toc: true
    css:
      - css/jhelvy.css
      - css/small-spacing.css
twitter:
  creator: "@JohnHelveston"
base_url: https://www.jhelvy.com
preview: images/helveston.png
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source(file.path("R", "functions.R"))
library(distilltools)
pubs <- readr::read_csv(here::here("content", "pubs.csv"))
```

<center>
`r gscholar_stats("https://scholar.google.com/citations?user=DY2D56IAAAAJ")`
</center>

`r aside_center("Source: Google Scholar")`

<center>
```{r, echo=FALSE}
icon_link(
    icon = "ai ai-google-scholar",
    text = "Google Scholar",
    url  = "https://scholar.google.com/citations?user=DY2D56IAAAAJ"
)
icon_link(
    icon = "ai ai-orcid",
    text = "ORCID",
    url  = "https://orcid.org/0000-0002-2657-9191"
)
icon_link(
    icon = "ai ai-researchgate",
    text = "Research Gate",
    url  = "https://www.researchgate.net/profile/John_Helveston"
)
```
</center>

<br>

(^†^indicates student advised by Helveston)

## Publications in Peer Reviewed Journals

`r make_pub_list(pubs, "peer_reviewed")`

## Working Papers & Papers Under Review

`r make_pub_list(pubs, "working")`

## Full-Length Peer-Reviewed Conference Publications

## Magazine Publications

## Books / Book Chapters

## Theses

## Reports, Articles for Non-Academic Audiences, and Other Publications

## Software

## Media Coverage
