---
title: "Projects"
description: A collection of some of my ongoing projects that may or may not be related to my research.
output:
  distill::distill_article:
    toc: false
twitter:
  creator: "@JohnHelveston"
base_url: https://jhelvy.github.io/
preview: images/helveston.png
---

<!-- Reduce spacing between titles and text -->
<style>
d-article h3 {
  margin: 5px 0 0 0;
}
d-article p {
  margin: 5px 0 0 0;
}
.container {
  overflow: hidden;
}

.filterDiv {
  float: left;
  background-color: #2196F3;
  color: #ffffff;
  width: 100px;
  line-height: 100px;
  text-align: center;
  margin: 2px;
  display: none; /* Hidden by default */
}

/* The "show" class is added to the filtered elements */
.show {
  display: block;
}

/* Style the buttons */
.btn {
  border: none;
  outline: none;
  padding: 12px 16px;
  background-color: #f1f1f1;
  cursor: pointer;
}

/* Add a light grey background on mouse-over */
.btn:hover {
  background-color: #ddd;
}

/* Add a dark background to the active button */
.btn.active {
  background-color: #666;
  color: white;
}
</style>

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source(file.path("R", "functions.R"))
```

```{r}
image_float_layout(
    src   = "images/hex/logitr.png",
    width = 140,
    float = "left",
    title = "### [logitr](https://jhelvy.github.io/logitr/)",
    text  = 'An R package for estimating multinomial (MNL) and mixed logit (MXL) models in R with "Preference" space or "Willingness-to-pay" (WTP) space utility parameterizations.'
)
```

```{r}
image_float_layout(
    src   = "images/hex/xaringanBuilder.png",
    width = 140,
    float = "left",
    title = "### [xaringanBuilder](https://jhelvy.github.io/xaringanBuilder/)",
    text  = 'An R package for building [xaringan slides](https://github.com/yihui/xaringan) into multiple outputs, including html, pdf, png, gif, pptx, and mp4.'
)
```

```{r}
image_float_layout(
    src   = "images/hex/conjointTools.png",
    width = 140,
    float = "left",
    title = "### [conjointTools](https://jhelvy.github.io/conjointTools/)",
    text  = 'An R package of tools for designing choice based conjoint survey experiments.'
)
```
