---
title: "Publications"
output:
  distill::distill_article:
    toc: true
twitter:
  creator: "@JohnHelveston"
base_url: https://jhelvy.github.io/
preview: images/helveston.png
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

source(file.path("R", "functions.R"))
cites <- get_cites()
```

<center>
Citations: `r cites$citations` | h-index: `r cites$hindex` | i10-index: `r cites$i10index`
</center>
<aside>Source: Google Scholar</aside>

<center>
```{r, echo=FALSE}
make_link_button(
    text = "Google Scholar",
    url  = "https://scholar.google.com/citations?user=DY2D56IAAAAJ",
    icon = "ai ai-google-scholar"
)
make_link_button(
    text = "ORCID",
    url  = "https://orcid.org/0000-0002-2657-9191",
    icon = "ai ai-orcid"
)
make_link_button(
    text = "Research Gate",
    url  = "https://www.researchgate.net/profile/John_Helveston",
    icon = "ai ai-researchgate"
)
```
</center>

## Publications in Peer Reviewed Journals

Feinberg, F., Bruch, E., Braun, M., Hemenway Falk, B., Fefferman, N., Feit, E.M., **Helveston, J.P.**, Larremore, D., McShane, B.B., Patania, A., & Small, M.L. (2020). "Choices in networks: a research framework." _Marketing Letters_. 31(4), 349-359.
`r make_doi("10.1007/s11002-020-09541-9")`

Roberson, Laura A. & **Helveston, John P.** (2020) "Electric vehicle adoption: can short experiences lead to big change?," _Environmental Research Letters_. 15(0940c3).
`r make_doi("10.1088/1748-9326/aba715")`

```{r, echo=FALSE}
make_link_button(
    text = "PDF",
    url  = "https://iopscience.iop.org/article/10.1088/1748-9326/aba715/pdf",
    icon = "fa fa-file-pdf"
)
make_link_button(
    text = "Code & Data",
    url  = "https://zenodo.org/badge/latestdoi/247706381",
    icon = "fab fa-github"
)
```

**Helveston, John P.** & Jonas Nahm (2019) "China's key role in scaling low-carbon energy technologies," _Science_, 366(6467), pg. 794-796.
`r make_doi("10.1126/science.aaz1014")`

```{r, echo=FALSE}
make_link_button(
    text = "PDF",
    url  = "https://science.sciencemag.org/content/sci/366/6467/794.full.pdf?ijkey=BpsTMIIAzoEgE&keytype=ref&siteid=sci",
    icon = "fa fa-file-pdf"
)
```

**Helveston, John P.**, Yanmin Wang, Valerie J. Karplus, & Erica R.H. Fuchs (2019) "Institutional Complementarities: The Origins of Experimentation in China’s Plug-in Electric Vehicle Industry," _Research Policy_, 48(1), pg. 206-222.
`r make_doi("10.1016/j.respol.2018.08.006")`

```{r, echo=FALSE}
make_link_button(
    text = "PDF",
    url  = "http://www.box.jhelvy.com/docs/papers/2019%20-%20Helveston%20et%20al%20-%20Institutional%20Complementarities%20-%20Research%20Policy.pdf",
    icon = "fa fa-file-pdf"
)
make_link_button(
    text = "SSRN",
    url  = "http://ssrn.com/abstract=2817052"
)
```

**Helveston, John P.**, Stephanie Seki, Jihoon Min, Evelyn Fairman, Arthur A. Boni, Jeremy J. Michalek, & Ines Azevedo (2019) "Choice at the Pump: Measuring Preferences for Lower-Carbon Combustion Fuels," _Environmental Research Letters_. 14(8)
`r make_doi("10.1088/1748-9326/ab2bd2")`

```{r, echo=FALSE}
make_link_button(
    text = "PDF",
    url  = "https://iopscience.iop.org/article/10.1088/1748-9326/ab2bd2/pdf",
    icon = "fa fa-file-pdf"
)
```

**Helveston, John P.**, Elea M. Feit, & Jeremy J. Michalek (2018) "Pooling Stated and Revealed Preference Data in the Presence of Endogeneity," _Transportation Research Part B: Methodological_, 109, pg. 70-89.
`r make_doi("10.1016/j.trb.2018.01.010")`

```{r, echo=FALSE}
make_link_button(
    text = "PDF",
    url  = "http://www.box.jhelvy.com/docs/papers/2018%20-%20Helveston%20et%20al%20-%20Pooling%20Stated%20and%20Revealed%20Preference%20Data.pdf",
    icon = "fa fa-file-pdf"
)
make_link_button(
    text = "Research Gate",
    url  = "https://www.researchgate.net/publication/323491265_Pooling_stated_and_revealed_preference_data_in_the_presence_of_RP_endogeneity",
    icon = "ai ai-researchgate"
)
```

**Helveston, John P.**, Yimin Liu, Elea M. Feit, Erica R.H. Fuchs, Erica Klampﬂ, & Jeremy J. Michalek (2015) "Will subsidies drive electric vehicle adoption? Measuring consumer preferences in the U.S. and China". _Transportation Research Part A: Policy and Practice_, 73, 96–112.
`r make_doi("10.1016/j.tra.2015.01.002")`

```{r, echo=FALSE}
make_link_button(
    text = "PDF",
    url  = "http://www.box.jhelvy.com/docs/papers/2015%20-%20Helveston%20et%20al%20-%20Will%20Subsidies%20Drive%20Electric%20Vehicle%20Adoption%20Measuring%20Consumer%20Preferences%20in%20the%20U.S.%20and%20China.pdf",
    icon = "fa fa-file-pdf"
)
make_link_button(
    text = "Code & Data",
    url  = "https://zenodo.org/badge/latestdoi/308370580",
    icon = "fab fa-github"
)
make_link_button(
    text = "Research Gate",
    url  = "https://www.researchgate.net/publication/272297857_Will_subsidies_drive_electric_vehicle_adoption_Measuring_consumer_preferences_in_the_US_and_China?ev=prf_high",
    icon = "ai ai-researchgate"
)
```

## Full-Length Peer-Reviewed Conference Publications

Liang, Z., Li, D., Fu, X., Beltekian, D., **Helveston, J.P.** (2018) "The Co-evolution of MNE R&D Strategies and China’s National Innovation System: A Case Study on Siemens." 2018 _IEEE International Symposium on Innovation and Entrepreneurship (TEMS-ISIE)_, Beijing. pp. 1-9.
`r make_doi("10.1109/TEMS-ISIE.2018.8478558")`

**Helveston, John P.**, Wang, Y., Karplus, V. J., & Fuchs, E.R. (2016) "Up, Down, and Sideways: Innovation in China and the Case of Plug-in Electric Vehicles." _Academy of Management Annual Meeting_. Anaheim, CA. Aug. 5.

```{r, echo=FALSE}
make_link_button(
    text = "Slides",
    url  = "http://www.box.jhelvy.com/slides/2016-AOM.pdf",
    icon = "fa fa-file-pdf"
)
```

**Helveston, John P.**, Liu, Y., Feit, E.M., Fuchs, E.R., Klampfl, E., & Michalek, J.J. (2014) "Will Subsidies Drive Electric Vehicle Adoption? Measuring Consumer Preferences in the U.S.and China." _Academy of Management Annual Meeting_. Philadelphia, PA. Aug. 5.

```{r, echo=FALSE}
make_link_button(
    text = "Slides",
    url  = "http://www.box.jhelvy.com/slides/2014-AOM.pdf",
    icon = "fa fa-file-pdf"
)
```

**Helveston, John P.**, Liu, Y., Feit, E.M., Fuchs, E.R., Klampfl, E., & Michalek, J.J. (2014) "Will Subsidies Drive Electric Vehicle Adoption? Measuring Consumer Preferences in the U.S. and China." _National Academies Transportation Research Board Annual Meeting_. Washington, D.C. Jan. 13.

```{r, echo=FALSE}
make_link_button(
    text = "Slides",
    url  = "http://www.box.jhelvy.com/slides/2014-TRB.pdf",
    icon = "fa fa-file-pdf"
)
```

## Magazine Publications

**Helveston, John P.** "Why the US Trails the World in Electric Vehicles," _Issues in Science and Technology_ 37, no. 2 (Winter 2021).

```{r, echo=FALSE}
make_link_button(
    text = "Open in new tab",
    url  = "https://issues.org/china-norway-ev-tesla/",
    icon = "fas fa-external-link-alt"
)
```

**Helveston, John P.** "Perspective: Navigating an Uncertain Future for US Roads," _Issues in Science and Technology_ 34, no. 1 (Fall 2017).

```{r, echo=FALSE}
make_link_button(
    text = "PDF",
    url  = "http://www.box.jhelvy.com/docs/papers/2017%20-%20Helveston%20-%20Navigating%20an%20Uncertain%20Future%20for%20US%20Roads%20(Fall%202017%20IST).pdf",
    icon = "fa fa-file-pdf"
)
make_link_button(
    text = "Open in new tab",
    url  = "http://issues.org/34-1/perspective-navigating-an-uncertain-future-for-us-roads/",
    icon = "fas fa-external-link-alt"
)
```

## Books / Book Chapters

Ren, Justin Z. & John P. Helveston (2019) "Measuring Electric Vehicle Infrastructure Among Cities: A Multi-Dimensional Approach." Melting the ICE: Lessons from China and the West in the Transition from the Internal Combustion Engine to Electric Vehicles. Ed. Fox-Penner, P., Ren, Z.J., & Jermain, D.O. Harvard University Press.

```{r, echo=FALSE}
make_link_button(
    text = "PDF",
    url  = "http://www.box.jhelvy.com/docs/papers/2019%20-%20MeltingIceBook_7.pdf",
    icon = "fa fa-file-pdf"
)
make_link_button(
    text = "Open in new tab",
    url  = "http://www.bu.edu/ise/research/meltingtheice/",
    icon = "fas fa-external-link-alt"
)
```

Hatch, Jennifer & John P. Helveston (2019) "Brookline, MA: A Small Town seeking to lead in a Broader EV Charging Network." Melting the ICE: Lessons from China and the West in the Transition from the Internal Combustion Engine to Electric Vehicles. Ed. Fox-Penner, P., Ren, Z.J., & Jermain, D.O. Harvard University Press.

```{r, echo=FALSE}
make_link_button(
    text = "PDF",
    url  = "http://www.box.jhelvy.com/docs/papers/2019%20-%20MeltingIceBook_6.pdf",
    icon = "fa fa-file-pdf"
)
make_link_button(
    text = "Open in new tab",
    url  = "http://www.bu.edu/ise/research/meltingtheice/",
    icon = "fas fa-external-link-alt"
)
```

## Working Papers

Murphree, Michael, John P. Helveston, & Daniel Breznitz. "Intellectual Property as a Production Input: Expanding Theories of Institutional Change and Profiting from Innovation." _Under review_.

Helveston, John P, Lujin Zhao, Saurav Pantha. "Are we there yet? The significance of arrival time uncertainty in multi-modal trip choices."

## Theses

**Helveston, John P.** (2016) "Development and Adoption of Plug-in Electric Vehicles in China: Markets, Policy, and Innovation," Ph.D. Dissertation, Carnegie Mellon University, Pittsburgh, PA.

```{r, echo=FALSE}
make_link_button(
    text = "PDF",
    url  = "http://www.box.jhelvy.com/docs/papers/2016%20-%20Helveston%20-%20Dissertation%20-%20Development%20and%20Adoption%20of%20Plug-in%20Electric%20Vehicles%20in%20China.pdf",
    icon = "fa fa-file-pdf"
)
make_link_button(
    text = "Research Gate",
    url  = "https://www.researchgate.net/publication/315897350_Development_and_Adoption_of_Plug-in_Electric_Vehicles_in_China_Markets_Policy_and_Innovation",
    icon = "ai ai-researchgate"
)
make_link_button(
    text = "CMU Repository",
    url  = "https://kilthub.cmu.edu/articles/Development_and_Adoption_of_Plug-in_Electric_Vehicles_in_China_Markets_Policy_and_Innovation/6715850",
    icon = "fas fa-external-link-alt"
)
```

## Reports, Articles for Non-Academic Audiences, and Other Publications

Podcast: GWU Professor **John Helveston** on EVs in China, _The Future Car: A Siemens Podcast_, May 13, 2019.

```{r, echo=FALSE}
make_link_button(
    text = "Listen",
    url  = "https://shows.pippa.io/the-future-car-a-siemens-podcast/episodes/john-helveston",
    icon = "fas fa-external-link-alt"
)
```

**Helveston, John P.** (2019) "China’s looser rules may usher in a new era for EV and AV companies," _Axios_. February 1, 2019.

```{r, echo=FALSE}
make_link_button(
    text = "Open in new tab",
    url  = "https://www.axios.com/chinas-looser-rules-may-usher-in-a-new-era-for-ev-and-av-companies-2ad9f9c2-2b0e-46c6-9b58-87f409159fff.html",
    icon = "fas fa-external-link-alt"
)
```

Hatch, Jennifer & **John P. Helveston**. "Will Autonomous Vehicles be Electric?" _Institute for Sustainable Energy_. August 8, 2018.

```{r, echo=FALSE}
make_link_button(
    text = "Open in new tab",
    url  = "https://www.bu.edu/ise/2018/08/27/will-autonomous-vehicles-be-electric/",
    icon = "fas fa-external-link-alt"
)
```

## Media Coverage

- Jul. 25, 2020 - Forbes, ["This Is A Big Reason Electric Cars Still Aren’t Popular With Americans: Study"](https://www.forbes.com/sites/brookecrothers/2020/07/25/one-huge-reason-electric-cars-still-arent-popular-with-americans-with-the-exception-of-the-tesla-model-3/#55c48a4955c1)
- Nov. 21, 2019 - NPR Climate Cast, ["Trade dispute with China could slow transition to low-carbon power"](https://www.mprnews.org/episode/2019/11/21/trade-dispute-with-china-could-slow-transition-to-lowcarbon-power)
- Nov. 15, 2019 - Xinhua news, ["美能源专家呼吁美加强与中国合作以实现减排目标"](http://www.xinhuanet.com/world/2019-11/15/c_1125235667.htm)
- Nov. 15, 2019 - Interview with GW Today, ["Collaboration with China Is Critical to Achieving Climate Goals"](https://gwtoday.gwu.edu/collaboration-china-critical-achieving-climate-goals)
- Oct. 28, 2019 - Physics World, ["US motorists prepared to pay more for fuel to lower emissions"](https://physicsworld.com/a/us-motorists-prepared-to-pay-more-for-fuel-to-lower-emissions/)
