---
title: "Research"
description: I study how consumers, firms, markets, and policy affect technological change, with a goal of facilitating transitions to sustainable, low-carbon technologies.
output:
  distill::distill_article:
    toc: true
    css:
      - css/jhelvy.css
      - css/small-spacing.css
twitter:
  creator: "@JohnHelveston"
base_url: https://www.jhelvy.com
preview: images/helveston.png
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source(file.path("R", "functions.R"))
library(distilltools)
pubs <- readr::read_csv(here::here("content", "pubs.csv"))
```

<center>
`r gscholar_stats("https://scholar.google.com/citations?user=DY2D56IAAAAJ")`
</center>

`r aside_center("Source: Google Scholar")`

<center>
```{r, echo=FALSE}
icon_link(
    icon = "ai ai-google-scholar",
    text = "Google Scholar",
    url  = "https://scholar.google.com/citations?user=DY2D56IAAAAJ"
)
icon_link(
    icon = "ai ai-orcid",
    text = "ORCID",
    url  = "https://orcid.org/0000-0002-2657-9191"
)
icon_link(
    icon = "ai ai-researchgate",
    text = "Research Gate",
    url  = "https://www.researchgate.net/profile/John_Helveston"
)
```
</center>

<br>

(^†^indicates student advised by Helveston)

## Publications in Peer Reviewed Journals

`r make_pub_list(pubs, "peer_reviewed")`

## Working Papers & Papers Under Review

`r make_pub_list(pubs, "working")`

## Full-Length Peer-Reviewed Conference Publications

## Magazine Publications

## Books / Book Chapters

## Theses

## Reports, Articles for Non-Academic Audiences, and Other Publications

## Software

## Media Coverage

- May 30, 2021 - The Wire China, quoted in ["The Competition Conundrum"](https://www.thewirechina.com/2021/05/30/the-competition-conundrum/)
- Apr. 23, 2021 - CNN Climate Town Hall, asked question to U.S. Secretary of State John Kerry [Watch](http://u.pc.cd/YTlctalK)
- Jul. 25, 2020 - Forbes, ["This Is A Big Reason Electric Cars Still Aren’t Popular With Americans: Study"](https://www.forbes.com/sites/brookecrothers/2020/07/25/one-huge-reason-electric-cars-still-arent-popular-with-americans-with-the-exception-of-the-tesla-model-3/#55c48a4955c1)
- Nov. 21, 2019 - NPR Climate Cast, ["Trade dispute with China could slow transition to low-carbon power"](https://www.mprnews.org/episode/2019/11/21/trade-dispute-with-china-could-slow-transition-to-lowcarbon-power)
- Nov. 15, 2019 - Xinhua news, ["美能源专家呼吁美加强与中国合作以实现减排目标"](http://www.xinhuanet.com/world/2019-11/15/c_1125235667.htm)
- Nov. 15, 2019 - Interview with GW Today, ["Collaboration with China Is Critical to Achieving Climate Goals"](https://gwtoday.gwu.edu/collaboration-china-critical-achieving-climate-goals)
- Oct. 28, 2019 - Physics World, ["US motorists prepared to pay more for fuel to lower emissions"](https://physicsworld.com/a/us-motorists-prepared-to-pay-more-for-fuel-to-lower-emissions/)
