---
title: "Research"
description: I study how consumers, firms, markets, and policy affect technological change, with a goal of facilitating transitions to sustainable, low-carbon technologies. I have expertise in choice modeling, programming in R, and qualitative research methods, as well as the global electric vehicle industry.
output:
  distill::distill_article:
    toc: true
    css:
      - css/jhelvy.css
      - css/small-spacing.css
twitter:
  creator: "@JohnHelveston"
base_url: https://www.jhelvy.com
preview: images/helveston.png
---

<!-- Remove margin under list items -->
<style>
d-article ol {
    margin-bottom: 5px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source(file.path("R", "functions.R"))
pubs <- get_pubs()
```

<center>
`r gscholar_stats("https://scholar.google.com/citations?user=DY2D56IAAAAJ")`
</center>

`r aside_center("Source: Google Scholar")`

<center>
```{r, echo=FALSE}
icon_link(
    icon = "ai ai-google-scholar",
    text = "Google Scholar",
    url  = "https://scholar.google.com/citations?user=DY2D56IAAAAJ"
)
icon_link(
    icon = "ai ai-orcid",
    text = "ORCID",
    url  = "https://orcid.org/0000-0002-2657-9191"
)
icon_link(
    icon = "ai ai-researchgate",
    text = "Research Gate",
    url  = "https://www.researchgate.net/profile/John_Helveston"
)
```
</center>

<br>

## Publications in Peer Reviewed Journals 

<aside>*indicates student advised by Helveston</aside>

`r make_pub_list(pubs, "peer_reviewed")`

## Working Papers & Papers Under Review

`r make_pub_list(pubs, "working")`

## Conference Publications

`r make_pub_list(pubs, "conference")`

## Magazine Publications

`r make_pub_list(pubs, "magazine")`

## Books / Book Chapters

`r make_pub_list(pubs, "book")`

## Theses

`r make_pub_list(pubs, "theses")`

## Reports, Articles for Non-Academic Audiences, and Other Publications

`r make_pub_list(pubs, "other")`

## Software

`r make_pub_list(pubs, "software")`

## Media Coverage

`r make_media_list()`
