---
title: "Obtaining Willingness to Pay Estimates from Preference Space and Willingness to Pay Space Utility Models"
description: |
  My talk for the 2021 Sawtooth Conference Turbo Choice Modeling Panel
author: John Paul Helveston
date: 04-20-2021
preview: "sawtooth-conf-logitr.png"
categories:
  - R
  - surveys
  - conjoint
twitter:
  creator: "@JohnHelveston"
output:
  distill::distill_article:
    self_contained: false
    toc: false
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE}
library(metathis)

knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.retina = 3,
  comment = "#>"
)

meta() %>%
  meta_description(
    'My talk for the 2021 Sawtooth Conference Turbo Choice Modeling Panel'
  ) %>%
  meta_name("github-repo" = "jhelvy/jhelvy.com") %>%
  meta_viewport() %>%
  meta_social(
    title = "Obtaining Willingness to Pay Estimates from Preference Space and Willingness to Pay Space Utility Models",
    url = "https://www.jhelvy.com/talks/2021-04-20-sawtooth-conf-logitr/",
    image = "https://www.jhelvy.com/talks/2021-04-20-sawtooth-conf-logitr/sawtooth-conf-logitr.png",
    image_alt = "Title slide for my talk",
    og_type = "website",
    og_author = c("John Paul Helveston"),
    twitter_card_type = "summary",
    twitter_creator = "@JohnHelveston"
  )

# Load button functions (eventually will replace this with {distilltools})
make_icon <- function(icon) {
  return(htmltools::tag("i", list(class = icon)))
}

make_icon_text <- function(icon, text) {
  return(htmltools::HTML(paste0(make_icon(icon), " ", text)))
}

icon_link <- function(icon = NULL, text = NULL, url = NULL) {
  if (!is.null(icon)) {
    text <- make_icon_text(icon, text)
  }
  return(htmltools::a(href = url, text, class = "icon-link"))
}
```

I gave a talk at the Sawtooth Software Conference [Turbo Choice Modeling Seminar](https://events.sawtoothsoftware.com/turboseminar) in San Antonio, Texas, April 19-23, 2021 (I pre-recorded my talk as I did not attend in-person). The talk is titled, "The [{logitr}](https://jhelvy.github.io/logitr/) R Package: Obtaining Willingness to Pay Estimates from Preference Space and Willingness to Pay Space Utility Models".

Learn more about the {logitr} package [here](https://jhelvy.github.io/logitr/).

# Slides

My slides were built using the [{xaringan}](https://github.com/yihui/xaringan) R package. You can see the source code for the slides [here](https://github.com/jhelvy/2021-sawtooth-conf).

```{r, echo=FALSE}
icon_link(
    icon = "fas fa-external-link-alt",
    text = "Full screen slides",
    url  = "https://jhelvy.github.io/2021-sawtooth-conf"
)
icon_link(
    icon = "fa fa-file-pdf",
    text = "Slides as PDF",
    url  = "https://github.com/jhelvy/2021-sawtooth-conf/raw/main/2021-sawtooth-conf.pdf"
)
```

Keyboard Shortcuts for Slides:

- Use <kbd>←</kbd> and <kbd>→</kbd> to navigate through the slides.
- Use <kbd>f</kbd> to toggle full screen.
- Use <kbd>o</kbd> to view an overview of all slides.
- Use <kbd>h</kbd> to see a list of other shortcuts.

```{r slides, echo=FALSE}
xaringanExtra::embed_xaringan(
  url = "https://jhelvy.github.io/2021-sawtooth-conf/index.html",
  ratio = "16:9")
```
