---
title: "U. Albany Confucius Institute Fall 2020 Seminar on US-China Relations in the 21st Century"
description: |
  My discussion with Barry Naughton (UCSD) about industrial policy and low-carbon energy technologies in China
author: John Paul Helveston
date: 10-09-2020
preview: "title_slide.png"
categories:
  - China
  - Technology
twitter:
  creator: "@JohnHelveston"
output:
  distill::distill_article:
    self_contained: false
    toc: false
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE}
library(metathis)
library(distilltools)

knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.retina = 3,
  comment = "#>"
)

meta() %>%
  meta_description(
    'My discussion with Barry Naughton (UCSD) about industrial policy and low-carbon energy technologies in China'
  ) %>%
  meta_viewport() %>%
  meta_social(
    title = "U. Albany Confucius Institute Fall 2020 Seminar on US-China Relations in the 21st Century",
    url = "https://www.jhelvy.com/talks/2020-10-09-confucius-institute-fall-seminar",
    image = "https://www.jhelvy.com/talks/2020-10-09-confucius-institute-fall-seminar/title_slide.png",
    image_alt = "Title slide showing pictures of me and Barry Naughton",
    og_type = "website",
    og_author = c("John Paul Helveston"),
    twitter_card_type = "summary",
    twitter_creator = "@JohnHelveston"
  )
```

[Barry Naughton](https://gps.ucsd.edu/faculty-directory/barry-naughton.html) (Sokwanlok Chair of Chinese International Affairs at the School of Global Policy and Strategy, UCSD) and I kicked off the U. of Albany [Confucius Institute Fall 2020 Seminar Series](https://www.albany.edu/confucius/US-china-relations-fall2020.html) on "_US-China Relations in the 21st Century_" with a discussion about industrial policy and low-carbon energy technologies in China. In his presentation titled, "_China's Industrial Policy: New Technological Revolution or Old-fashioned Protectionism?_", Professor Naughton highlighted some of the recent major technology and industrial policy changes under President Xi and the implications for the U.S. In my talk titled, "_China's key role in scaling low carbon energy technologies_," I discussed the critical role China has played in scaling up the mass production of low-carbon energy technologies, such as solar photovoltaic cells and lithium-ion batteries, highlighting key points from my related [paper in _Science_](https://iopscience.iop.org/article/10.1088/1748-9326/aba715/pdf) with Jonas Nahm.

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "Slides as PDF",
    url  = "https://filedn.com/lYURdAnVcCykBHec07i0c6j/slides/2020_10_09_helveston_confucius_institute.pdf"
)
icon_link(
    icon = "fa fa-file-pdf",
    text = "Science Paper",
    url  = "https://iopscience.iop.org/article/10.1088/1748-9326/aba715/pdf"
)
```

<iframe width="640" height="600" src="https://u.pcloud.link/publink/show?code=XZqIdeXZCh4KxAo6M10nFln5MelSvSkmh117" frameborder="0" allow="accelerometer; encrypted-media; gyroscope; picture-in-picture" allowfullscreen scrolling="no"></iframe>
